\vspace{-2cm}A generative model for urban firm networks

### 2020-09-11 S1_Text.tex
Update on Overleaf.
SuppMat

\input{si.tex}
\begin{document}
\vspace*{0.35in}
\justify

@@

When considering the UK sectors generating the highest turnover in 2018 mostly dependent on foreign capital they own (out-going links from the UK) these are extraction of crude petroleum, manufacture of tobacco products and of basic pharmaceutical goods. In terms of in-going links to the UK, activities of head offices and holding companies, sale of cars and manufacture of motor vehicles are sectors mostly dependent on foreign ownership coming from abroad.

@@

\newpage
When expressed in total number of links, activities mostly dependent on out-going links from the UK are activities of holding companies, of head offices and fund management activities. In terms of in-going links these are business and consultancy activities and renting and operating of own and leased real estate.

>>>>

\input{si.tex}

\renewcommand{\thetable}{S1-\Alph{table}}

\begin{document}
\vspace*{0.35in}
\justify

@@

When considering the UK sectors generating the highest turnover in 2018 mostly dependent on foreign capital they own (out-going links from the UK - see below Table~\ref{tab:uk_outgoing}) these are extraction of crude petroleum, manufacture of tobacco products and of basic pharmaceutical goods. In terms of in-going links to the UK (see below Table~\ref{tab:uk_ingoing}), activities of head offices and holding companies, sale of cars and manufacture of motor vehicles are sectors mostly dependent on foreign ownership coming from abroad.

@@

\newpage
When expressed in total number of links (Table~\ref{tab:uk_outgoinglinks} and Table~\ref{tab:uk_ingoinglinks}), activities mostly dependent on out-going links from the UK are activities of holding companies, of head offices and fund management activities. In terms of in-going links these are business and consultancy activities and renting and operating of own and leased real estate.

### 2020-09-11 S2_Text.tex
SuppMat

The procedure for the synthetic sector setup is the following:
\begin{itemize}
    \item Sectors distributions follow log-normal densities with most mass in $\left[0;1\right]$
    \item Large cities are more innovative and more diverse. Assuming that sectors are ordered by innovativity (the larger the sector index the larger the innovativity), this assumption is translated by taking a mode and variance of 0.5 for the largest city and a mode and variance of $1/K$ for the smallest, and a linear interpolation between the two. For each city, we define
    \[
    \log(e_i) = \frac{(\log(E_i) - \log(E_{imin}))}{(\log(E_{imax}) - \log(E_{imin}))} * (1/2 - 1/K) + 1/K
    \]
    \item Log-normal parameters for each city are then fixed by $mu_i - sigma_i^2 = log(e_i)$ and $-3 sigma_i^2 - 2 log(exp(sigma_i^2) - 1) = log(e_i)$
    \item $\sigma_i^2$ is the unique positive root of $f(X)=0$ with $f(X) = -3X - 2 ln(exp(X) - 1) - ln(e_i)$
\end{itemize}

>>>>

The procedure for the synthetic sector setup is the following:
\begin{itemize}
    \item Sectors distributions follow log-normal densities with most mass in $\left[0;1\right]$
    \item Large cities are more innovative and more diverse. Assuming that sectors are ordered by innovativity (the larger the sector index the larger the innovativity), this assumption is translated by taking a mode and variance of 0.5 for the largest city and a mode and variance of $1/K$ for the smallest, and a linear interpolation between the two. For each city, we define
    \[
    \log(e_i) = \frac{(\log(E_i) - \log(E_{imin}))}{(\log(E_{imax}) - \log(E_{imin}))} * (1/2 - 1/K) + 1/K
    \]
    \item Log-normal parameters $(\mu_i,\sigma_i)$ for each city are then fixed by $\mu_i - \sigma_i^2 = \log(e_i)$ and $-3 \sigma_i^2 - 2 \log(\exp(\sigma_i^2) - 1) = log(e_i)$
    \item $\sigma_i^2$ is the unique positive root of $f(X)=0$ with $f(X) = -3X - 2 \log(\exp(X) - 1) - \log(e_i)$ and $\mu_i = \log(e_i) + \sigma_i^2$.
\end{itemize}
